---
title: "STA305 tech report"
author: "Parth Brahmbhatt"
date: "March 29, 2021"
output:
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Importing the data
This is the data we will use, it contains all the stores with blocking as well as the nutritional information and its Price_per_Z_mL.
```{r}
data <- readxl::read_excel("Data.xlsx", sheet = "All Stores with Stores Block")

colnames(data) <- gsub(" ", "_", colnames(data))
colnames(data) <- gsub("\\(|\\)", "", colnames(data))
```

### Background
With the information presented below, we will check whether the data satisfies the assumptions of Guass-markov assumptions as well as the assumptions of linear regression.

### Scatterplot
## Walmart
# Price_per_Z_mL vs Calories
```{r}
model <- lm(Price_per_Z_mL ~ Calories_per_Z_mL, data=subset(data, Store == 'Walmart'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Calories_per_Z_mL, main="Price_per_Z_mL vs Calories for Walmart", data=subset(data, Store == 'Walmart'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Fat (g)
```{r}
model <- lm(Price_per_Z_mL ~ Fat_g_per_Z_mL, data=subset(data, Store == 'Walmart'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Fat_g_per_Z_mL, main="Price_per_Z_mL vs Fat (g) for Walmart", data=subset(data, Store == 'Walmart'))
```


# Price_per_Z_mL vs Sodium (mg)
```{r}
model <- lm(Price_per_Z_mL ~ Sodium_mg_per_Z_mL, data=subset(data, Store == 'Walmart'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Sodium_mg_per_Z_mL, main="Price_per_Z_mL vs Sodium (mg) for Walmart", data=subset(data, Store == 'Walmart'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Carbohydrates (g)
```{r}
model <- lm(Price_per_Z_mL ~ Carbohydrates_g_per_Z_mL, data=subset(data, Store == 'Walmart'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Carbohydrates_g_per_Z_mL, main="Price_per_Z_mL vs Carbohydrates (g) for Walmart", data=subset(data, Store == 'Walmart'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Sugars (g)
```{r}
model <- lm(Price_per_Z_mL ~ Sugars_g_per_Z_mL, data=subset(data, Store == 'Walmart'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Sugars_g_per_Z_mL, main="Price_per_Z_mL vs Sugars (g) for Walmart", data=subset(data, Store == 'Walmart'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Protein (g)
```{r}
model <- lm(Price_per_Z_mL ~ Protein_g_per_Z_mL, data=subset(data, Store == 'Walmart'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Protein_g_per_Z_mL, main="Price_per_Z_mL vs Protein (g) for Walmart", data=subset(data, Store == 'Walmart'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```












## Zehrs
# Price_per_Z_mL vs Calories
```{r}
model <- lm(Price_per_Z_mL ~ Calories_per_Z_mL, data=subset(data, Store == 'Zehrs'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Calories_per_Z_mL, main="Price_per_Z_mL vs Calories for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Fat (g)
```{r}
model <- lm(Price_per_Z_mL ~ Fat_g_per_Z_mL, data=subset(data, Store == 'Zehrs'))

plot(Price_per_Z_mL ~ Fat_g_per_Z_mL, main="Price_per_Z_mL vs Fat (g) for Zehrs", data=subset(data, Store == 'Zehrs'))
```


# Price_per_Z_mL vs Sodium (mg)
```{r}
model <- lm(Price_per_Z_mL ~ Sodium_mg_per_Z_mL, data=subset(data, Store == 'Zehrs'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Sodium_mg_per_Z_mL, main="Price_per_Z_mL vs Sodium (mg) for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Carbohydrates (g)
```{r}
model <- lm(Price_per_Z_mL ~ Carbohydrates_g_per_Z_mL, data=subset(data, Store == 'Zehrs'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Carbohydrates_g_per_Z_mL, main="Price_per_Z_mL vs Carbohydrates (g) for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Sugars (g)
```{r}
model <- lm(Price_per_Z_mL ~ Sugars_g_per_Z_mL, data=subset(data, Store == 'Zehrs'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Sugars_g_per_Z_mL, main="Price_per_Z_mL vs Sugars (g) for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Protein (g)
```{r}
model <- lm(Price_per_Z_mL ~ Protein_g_per_Z_mL, data=subset(data, Store == 'Zehrs'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Protein_g_per_Z_mL, main="Price_per_Z_mL vs Protein (g) for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```






## Metro
# Price_per_Z_mL vs Calories
```{r}
model <- lm(Price_per_Z_mL ~ Calories_per_Z_mL, data=subset(data, Store == 'Metro'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Calories_per_Z_mL, main="Price_per_Z_mL vs Calories for Metro", data=subset(data, Store == 'Metro'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Fat (g)
```{r}
model <- lm(Price_per_Z_mL ~ Fat_g_per_Z_mL, data=subset(data, Store == 'Metro'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Fat_g_per_Z_mL, main="Price_per_Z_mL vs Fat (g) for Metro", data=subset(data, Store == 'Metro'))
```


# Price_per_Z_mL vs Sodium (mg)
```{r}
model <- lm(Price_per_Z_mL ~ Sodium_mg_per_Z_mL, data=subset(data, Store == 'Metro'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Sodium_mg_per_Z_mL, main="Price_per_Z_mL vs Sodium (mg) for Metro", data=subset(data, Store == 'Metro'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Carbohydrates (g)
```{r}
model <- lm(Price_per_Z_mL ~ Carbohydrates_g_per_Z_mL, data=subset(data, Store == 'Metro'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Carbohydrates_g_per_Z_mL, main="Price_per_Z_mL vs Carbohydrates (g) for Metro", data=subset(data, Store == 'Metro'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Sugars (g)
```{r}
model <- lm(Price_per_Z_mL ~ Sugars_g_per_Z_mL, data=subset(data, Store == 'Metro'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Sugars_g_per_Z_mL, main="Price_per_Z_mL vs Sugars (g) for Metro", data=subset(data, Store == 'Metro'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Protein (g)
```{r}
model <- lm(Price_per_Z_mL ~ Protein_g_per_Z_mL, data=subset(data, Store == 'Metro'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Protein_g_per_Z_mL, main="Price_per_Z_mL vs Protein (g) for Metro", data=subset(data, Store == 'Metro'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```







## No Frills
# Price_per_Z_mL vs Calories
```{r}
model <- lm(Price_per_Z_mL ~ Calories_per_Z_mL, data=subset(data, Store == 'No-Frills'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Calories_per_Z_mL, main="Price_per_Z_mL vs Calories for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Fat (g)
```{r}
model <- lm(Price_per_Z_mL ~ Fat_g_per_Z_mL, data=subset(data, Store == 'No-Frills'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Fat_g_per_Z_mL, main="Price_per_Z_mL vs Fat (g) for No-Frills", data=subset(data, Store == 'No-Frills'))
```


# Price_per_Z_mL vs Sodium (mg)
```{r}
model <- lm(Price_per_Z_mL ~ Sodium_mg_per_Z_mL, data=subset(data, Store == 'No-Frills'))

plot(Price_per_Z_mL ~ Sodium_mg_per_Z_mL, main="Price_per_Z_mL vs Sodium (mg) for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Carbohydrates (g)
```{r}
model <- lm(Price_per_Z_mL ~ Carbohydrates_g_per_Z_mL, data=subset(data, Store == 'No-Frills'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Carbohydrates_g_per_Z_mL, main="Price_per_Z_mL vs Carbohydrates (g) for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Sugars (g)
```{r}
model <- lm(Price_per_Z_mL ~ Sugars_g_per_Z_mL, data=subset(data, Store == 'No-Frills'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Sugars_g_per_Z_mL, main="Price_per_Z_mL vs Sugars (g) for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Protein (g)
```{r}
model <- lm(Price_per_Z_mL ~ Protein_g_per_Z_mL, data=subset(data, Store == 'No-Frills'))

summary(model)
anova(model)

plot(Price_per_Z_mL ~ Protein_g_per_Z_mL, main="Price_per_Z_mL vs Protein (g) for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```







### Residual
## Walmart
# Price_per_Z_mL vs Calories
```{r}
model <- lm(Price_per_Z_mL ~ Calories_per_Z_mL, data=subset(data, Store == 'Walmart'))

res <- rstandard(model)

plot(res ~ Calories_per_Z_mL, main="Model residual vs Calories for Walmart", ylab="std.residuals", data=subset(data, Store == 'Walmart'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Fat (g)
```{r}
model <- lm(Price_per_Z_mL ~ Fat_g_per_Z_mL, data=subset(data, Store == 'Walmart'))

res <- rstandard(model)

plot(res ~ Fat_g_per_Z_mL, main="Model residual vs Fat (g) for Walmart", ylab="std.residuals", data=subset(data, Store == 'Walmart'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Sodium (mg)
```{r}
model <- lm(Price_per_Z_mL ~ Sodium_mg_per_Z_mL, data=subset(data, Store == 'Walmart'))

res <- rstandard(model)

plot(res ~ Sodium_mg_per_Z_mL, main="Model residual vs Sodium (mg) for Walmart",
ylab="std.residuals", data=subset(data, Store == 'Walmart'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price_per_Z_mL vs Carbohydrates (g)
```{r}
model <- lm(Price_per_Z_mL ~ Carbohydrates_g_per_Z_mL, data=subset(data, Store == 'Walmart'))

res <- rstandard(model)

plot(res ~ Carbohydrates_g_per_Z_mL, main="Model residual vs Carbohydrates (g) for Walmart", ylab="std.residuals", data=subset(data, Store == 'Walmart'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Sugars (g)
```{r}
model <- lm(Price_per_Z_mL ~ Sugars_g_per_Z_mL, data=subset(data, Store == 'Walmart'))

res <- rstandard(model)

plot(res ~ Sugars_g_per_Z_mL, main="Model residual vs Sugars (g) for Walmart", ylab="std.residuals", data=subset(data, Store == 'Walmart'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Protein (g)
```{r}
model <- lm(Price_per_Z_mL ~ Protein_g_per_Z_mL, data=subset(data, Store == 'Walmart'))

res <- rstandard(model)

plot(res ~ Protein_g_per_Z_mL, ylab="std.residuals", main="Model residual vs Protein (g) for Walmart", data=subset(data, Store == 'Walmart'))

abline(h = 0, lty = 2)
```












## Zehrs
# Price_per_Z_mL vs Calories
```{r}
model <- lm(Price_per_Z_mL ~ Calories_per_Z_mL, data=subset(data, Store == 'Zehrs'))

res <- rstandard(model)

plot(res ~ Calories_per_Z_mL, ylab="std.residuals", main="Model residual vs Calories for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Fat (g)
```{r}
model <- lm(Price_per_Z_mL ~ Fat_g_per_Z_mL, data=subset(data, Store == 'Zehrs'))

res <- rstandard(model)

plot(res ~ Fat_g_per_Z_mL, ylab="std.residuals", main="Model residual vs Fat (g) for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Sodium (mg)
```{r}
model <- lm(Price_per_Z_mL ~ Sodium_mg_per_Z_mL, data=subset(data, Store == 'Zehrs'))

res <- rstandard(model)

plot(res ~ Sodium_mg_per_Z_mL, ylab="std.residuals", main="Model residual vs Sodium (mg) for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Carbohydrates (g)
```{r}
model <- lm(Price_per_Z_mL ~ Carbohydrates_g_per_Z_mL, data=subset(data, Store == 'Zehrs'))

res <- rstandard(model)

plot(res ~ Carbohydrates_g_per_Z_mL, ylab="std.residuals", main="Model residual vs Carbohydrates (g) for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Sugars (g)
```{r}
model <- lm(Price_per_Z_mL ~ Sugars_g_per_Z_mL, data=subset(data, Store == 'Zehrs'))

res <- rstandard(model)

plot(res ~ Sugars_g_per_Z_mL, ylab="std.residuals", main="Model residual vs Sugars (g) for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Protein (g)
```{r}
model <- lm(Price_per_Z_mL ~ Protein_g_per_Z_mL, data=subset(data, Store == 'Zehrs'))

res <- rstandard(model)

plot(res ~ Protein_g_per_Z_mL, ylab="std.residuals", main="Model residual vs Protein (g) for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(h = 0, lty = 2)
```






## Metro
# Price_per_Z_mL vs Calories
```{r}
model <- lm(Price_per_Z_mL ~ Calories_per_Z_mL, data=subset(data, Store == 'Metro'))

res <- rstandard(model)

plot(res ~ Calories_per_Z_mL, ylab="std.residuals", main="Model residual vs Calories for Metro", data=subset(data, Store == 'Metro'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Fat (g)
```{r}
model <- lm(Price_per_Z_mL ~ Fat_g_per_Z_mL, data=subset(data, Store == 'Metro'))

res <- rstandard(model)

plot(res ~ Fat_g_per_Z_mL, ylab="std.residuals", main="Model residual vs Fat (g) for Metro", data=subset(data, Store == 'Metro'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Sodium (mg)
```{r}
model <- lm(Price_per_Z_mL ~ Sodium_mg_per_Z_mL, data=subset(data, Store == 'Metro'))

res <- rstandard(model)

plot(res ~ Sodium_mg_per_Z_mL, ylab="std.residuals", main="Model residual vs Sodium (mg) for Metro", data=subset(data, Store == 'Metro'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Carbohydrates (g)
```{r}
model <- lm(Price_per_Z_mL ~ Carbohydrates_g_per_Z_mL, data=subset(data, Store == 'Metro'))

res <- rstandard(model)

plot(res ~ Carbohydrates_g_per_Z_mL, ylab="std.residuals", main="Model residual vs Carbohydrates (g) for Metro", data=subset(data, Store == 'Metro'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Sugars (g)
```{r}
model <- lm(Price_per_Z_mL ~ Sugars_g_per_Z_mL, data=subset(data, Store == 'Metro'))

res <- rstandard(model)

plot(res ~ Sugars_g_per_Z_mL, ylab="std.residuals", main="Model residual vs Sugars (g) for Metro", data=subset(data, Store == 'Metro'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Protein (g)
```{r}
model <- lm(Price_per_Z_mL ~ Protein_g_per_Z_mL, data=subset(data, Store == 'Metro'))

res <- rstandard(model)

plot(res ~ Protein_g_per_Z_mL, ylab="std.residuals", main="Model residual vs Protein (g) for Metro", data=subset(data, Store == 'Metro'))

abline(h = 0, lty = 2)
```







## No-frills
# Price_per_Z_mL vs Calories
```{r}
model <- lm(Price_per_Z_mL ~ Calories_per_Z_mL, data=subset(data, Store == 'No-Frills'))

res <- rstandard(model)

plot(res ~ Calories_per_Z_mL, ylab="std.residuals", main="Model residual vs Calories for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Fat (g)
```{r}
model <- lm(Price_per_Z_mL ~ Fat_g_per_Z_mL, data=subset(data, Store == 'No-Frills'))

res <- rstandard(model)

plot(res ~ Fat_g_per_Z_mL, ylab="std.residuals", main="Model residual vs Fat (g) for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Sodium (mg)
```{r}
model <- lm(Price_per_Z_mL ~ Sodium_mg_per_Z_mL, data=subset(data, Store == 'No-Frills'))

res <- rstandard(model)

plot(res ~ Sodium_mg_per_Z_mL, ylab="std.residuals", main="Model residual vs Sodium (mg) for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Carbohydrates (g)
```{r}
model <- lm(Price_per_Z_mL ~ Carbohydrates_g_per_Z_mL, data=subset(data, Store == 'No-Frills'))

res <- rstandard(model)

plot(res ~ Carbohydrates_g_per_Z_mL, ylab="std.residuals", main="Model residual vs Carbohydrates (g) for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Sugars (g)
```{r}
model <- lm(Price_per_Z_mL ~ Sugars_g_per_Z_mL, data=subset(data, Store == 'No-Frills'))

res <- rstandard(model)

plot(res ~ Sugars_g_per_Z_mL, ylab="std.residuals", main="Model residual vs Sugars (g) for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(h = 0, lty = 2)
```


# Price_per_Z_mL vs Protein (g)
```{r}
model <- lm(Price_per_Z_mL ~ Protein_g_per_Z_mL, data=subset(data, Store == 'No-Frills'))

res <- rstandard(model)

plot(res ~ Protein_g_per_Z_mL, ylab="std.residuals", main="Model residual vs Protein (g) for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(h = 0, lty = 2)
```












### QQplots
## Walmart
# Price_per_Z_mL vs Calories
```{r}
model <- lm(Price_per_Z_mL ~ Calories_per_Z_mL, data=subset(data, Store == 'Walmart'))

qqnorm(residuals(model), main="Normal QQ-plot of Calories for Walmart")
qqline(residuals(model))
```


# Price_per_Z_mL vs Fat (g)
```{r}
model <- lm(Price_per_Z_mL ~ Fat_g_per_Z_mL, data=subset(data, Store == 'Walmart'))

qqnorm(residuals(model), main="Normal QQ-plot of Fat for Walmart")
qqline(residuals(model))
```


# Price_per_Z_mL vs Sodium (mg)
```{r}
model <- lm(Price_per_Z_mL ~ Sodium_mg_per_Z_mL, data=subset(data, Store == 'Walmart'))

qqnorm(residuals(model), main="Normal QQ-plot of Sodium for Walmart")
qqline(residuals(model))
```


# Price_per_Z_mL vs Carbohydrates (g)
```{r}
model <- lm(Price_per_Z_mL ~ Carbohydrates_g_per_Z_mL, data=subset(data, Store == 'Walmart'))

qqnorm(residuals(model), main="Normal QQ-plot of Carbohydrates for Walmart")
qqline(residuals(model))
```


# Price_per_Z_mL vs Sugars (g)
```{r}
model <- lm(Price_per_Z_mL ~ Sugars_g_per_Z_mL, data=subset(data, Store == 'Walmart'))

qqnorm(residuals(model), main="Normal QQ-plot of Sugars for Walmart")
qqline(residuals(model))
```


# Price_per_Z_mL vs Protein (g)
```{r}
model <- lm(Price_per_Z_mL ~ Protein_g_per_Z_mL, data=subset(data, Store == 'Walmart'))

qqnorm(residuals(model), main="Normal QQ-plot of Protein for Walmart")
qqline(residuals(model))
```












## Zehrs
# Price_per_Z_mL vs Calories
```{r}
model <- lm(Price_per_Z_mL ~ Calories_per_Z_mL, data=subset(data, Store == 'Zehrs'))

qqnorm(residuals(model), main="Normal QQ-plot of Calories for Zehrs")
qqline(residuals(model))
```


# Price_per_Z_mL vs Fat (g)
```{r}
model <- lm(Price_per_Z_mL ~ Fat_g_per_Z_mL, data=subset(data, Store == 'Zehrs'))

qqnorm(residuals(model), main="Normal QQ-plot of Fat for Zehrs")
qqline(residuals(model))
```


# Price_per_Z_mL vs Sodium (mg)
```{r}
model <- lm(Price_per_Z_mL ~ Sodium_mg_per_Z_mL, data=subset(data, Store == 'Zehrs'))

qqnorm(residuals(model), main="Normal QQ-plot of Sodium for Zehrs")
qqline(residuals(model))
```


# Price_per_Z_mL vs Carbohydrates (g)
```{r}
model <- lm(Price_per_Z_mL ~ Carbohydrates_g_per_Z_mL, data=subset(data, Store == 'Zehrs'))

qqnorm(residuals(model), main="Normal QQ-plot of Carbohydrates for Zehrs")
qqline(residuals(model))
```


# Price_per_Z_mL vs Sugars (g)
```{r}
model <- lm(Price_per_Z_mL ~ Sugars_g_per_Z_mL, data=subset(data, Store == 'Zehrs'))

qqnorm(residuals(model), main="Normal QQ-plot of Sugars for Zehrs")
qqline(residuals(model))
```


# Price_per_Z_mL vs Protein (g)
```{r}
model <- lm(Price_per_Z_mL ~ Protein_g_per_Z_mL, data=subset(data, Store == 'Zehrs'))

qqnorm(residuals(model), main="Normal QQ-plot of Protein for Zehrs")
qqline(residuals(model))
```






## Metro
# Price_per_Z_mL vs Calories
```{r}
model <- lm(Price_per_Z_mL ~ Calories_per_Z_mL, data=subset(data, Store == 'Metro'))

qqnorm(residuals(model), main="Normal QQ-plot of Calories for Metro")
qqline(residuals(model))
```


# Price_per_Z_mL vs Fat (g)
```{r}
model <- lm(Price_per_Z_mL ~ Fat_g_per_Z_mL, data=subset(data, Store == 'Metro'))

qqnorm(residuals(model), main="Normal QQ-plot of Fat for Metro")
qqline(residuals(model))
```


# Price_per_Z_mL vs Sodium (mg)
```{r}
model <- lm(Price_per_Z_mL ~ Sodium_mg_per_Z_mL, data=subset(data, Store == 'Metro'))

qqnorm(residuals(model), main="Normal QQ-plot of Sodium for Metro")
qqline(residuals(model))
```


# Price_per_Z_mL vs Carbohydrates (g)
```{r}
model <- lm(Price_per_Z_mL ~ Carbohydrates_g_per_Z_mL, data=subset(data, Store == 'Metro'))

qqnorm(residuals(model), main="Normal QQ-plot of Carbohydrates for Metro")
qqline(residuals(model))
```


# Price_per_Z_mL vs Sugars (g)
```{r}
model <- lm(Price_per_Z_mL ~ Sugars_g_per_Z_mL, data=subset(data, Store == 'Metro'))

qqnorm(residuals(model), main="Normal QQ-plot of Sugar for Metro")
qqline(residuals(model))
```


# Price_per_Z_mL vs Protein (g)
```{r}
model <- lm(Price_per_Z_mL ~ Protein_g_per_Z_mL, data=subset(data, Store == 'Metro'))

qqnorm(residuals(model), main="Normal QQ-plot of Protein for Metro")
qqline(residuals(model))
```







## No-frills
# Price_per_Z_mL vs Calories
```{r}
model <- lm(Price_per_Z_mL ~ Calories_per_Z_mL, data=subset(data, Store == 'No-Frills'))

qqnorm(residuals(model), main="Normal QQ-plot of Calories for No-frills")
qqline(residuals(model))
```


# Price_per_Z_mL vs Fat (g)
```{r}
model <- lm(Price_per_Z_mL ~ Fat_g_per_Z_mL, data=subset(data, Store == 'No-Frills'))

qqnorm(residuals(model), main="Normal QQ-plot of Fat for No-frills")
qqline(residuals(model))
```


# Price_per_Z_mL vs Sodium (mg)
```{r}
model <- lm(Price_per_Z_mL ~ Sodium_mg_per_Z_mL, data=subset(data, Store == 'No-Frills'))

qqnorm(residuals(model), main="Normal QQ-plot of Sodium for No-frills")
qqline(residuals(model))
```


# Price_per_Z_mL vs Carbohydrates (g)
```{r}
model <- lm(Price_per_Z_mL ~ Carbohydrates_g_per_Z_mL, data=subset(data, Store == 'No-Frills'))

qqnorm(residuals(model), main="Normal QQ-plot of Carbohydrates for No-frills")
qqline(residuals(model))
```


# Price_per_Z_mL vs Sugars (g)
```{r}
model <- lm(Price_per_Z_mL ~ Sugars_g_per_Z_mL, data=subset(data, Store == 'No-Frills'))

qqnorm(residuals(model), main="Normal QQ-plot of Sugar for No-frills")
qqline(residuals(model))
```


# Price_per_Z_mL vs Protein (g)
```{r}
model <- lm(Price_per_Z_mL ~ Protein_g_per_Z_mL, data=subset(data, Store == 'No-Frills'))

qqnorm(residuals(model), main="Normal QQ-plot of Protein for No-frills")
qqline(residuals(model))
```

