---
title: "STA305 tech report"
author: "Parth Brahmbhatt"
date: "March 29, 2021"
output:
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Importing the data
This is the data we will use, it contains all the stores with blocking as well as the nutritional information and its price.
```{r}
data <- readxl::read_excel("Data.xlsx", sheet = "All Stores with Stores Block")

colnames(data) <- gsub(" ", "_", colnames(data))
colnames(data) <- gsub("\\(|\\)", "", colnames(data))
```

### Background
With the information presented below, we will check whether the data satisfies the assumptions of Guass-markov assumptions as well as the assumptions of linear regression.

## Walmart
# Price vs Volume per unit (mL)
```{r}
model <- lm(Price ~ Volume_per_unit_mL, data=subset(data, Store == 'Walmart'))

plot(Price ~ Volume_per_unit_mL, main="Price vs Volume per unit (mL) for Walmart", data=subset(data, Store == 'Walmart'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Total Volume (mL)
```{r}
model <- lm(Price ~ Total_Vol_mL, data=subset(data, Store == 'Walmart'))

plot(Price ~ Total_Vol_mL, main="Price vs Total Volume (mL) for Walmart", data=subset(data, Store == 'Walmart'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Nutritional Value Base (mL)
```{r}
model <- lm(Price ~ Nutritional_Value_Base_mL, data=subset(data, Store == 'Walmart'))

plot(Price ~ Nutritional_Value_Base_mL, main="Price vs Nutritional Value Base (mL) for Walmart", data=subset(data, Store == 'Walmart'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Calories
```{r}
model <- lm(Price ~ NV_Calories, data=subset(data, Store == 'Walmart'))

plot(Price ~ NV_Calories, main="Price vs Calories for Walmart", data=subset(data, Store == 'Walmart'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Fat (g)
```{r}
model <- lm(Price ~ NV_Fat_g, data=subset(data, Store == 'Walmart'))

plot(Price ~ NV_Fat_g, main="Price vs Fat (g) for Walmart", data=subset(data, Store == 'Walmart'))
```


# Price vs Sodium (mg)
```{r}
model <- lm(Price ~ NV_Sodium_mg, data=subset(data, Store == 'Walmart'))

plot(Price ~ NV_Sodium_mg, main="Price vs Sodium (mg) for Walmart", data=subset(data, Store == 'Walmart'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Carbohydrates (g)
```{r}
model <- lm(Price ~ NV_Carbohydrates_g, data=subset(data, Store == 'Walmart'))

plot(Price ~ NV_Carbohydrates_g, main="Price vs Carbohydrates (g) for Walmart", data=subset(data, Store == 'Walmart'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Sugars (g)
```{r}
model <- lm(Price ~ NV_Sugars_g, data=subset(data, Store == 'Walmart'))

plot(Price ~ NV_Sugars_g, main="Price vs Sugars (g) for Walmart", data=subset(data, Store == 'Walmart'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Protein (g)
```{r}
model <- lm(Price ~ NV_Protein_g, data=subset(data, Store == 'Walmart'))

plot(Price ~ NV_Protein_g, main="Price vs Protein (g) for Walmart", data=subset(data, Store == 'Walmart'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```















## Zehrs
# Price vs Volume per unit (mL)
```{r}
model <- lm(Price ~ Volume_per_unit_mL, data=subset(data, Store == 'Zehrs'))

plot(Price ~ Volume_per_unit_mL, main="Price vs Volume per unit (mL) for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Total Volume (mL)
```{r}
model <- lm(Price ~ Total_Vol_mL, data=subset(data, Store == 'Zehrs'))

plot(Price ~ Total_Vol_mL, main="Price vs Total Volume (mL) for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Nutritional Value Base (mL)
```{r}
model <- lm(Price ~ Nutritional_Value_Base_mL, data=subset(data, Store == 'Zehrs'))

plot(Price ~ Nutritional_Value_Base_mL, main="Price vs Nutritional Value Base (mL) for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Calories
```{r}
model <- lm(Price ~ NV_Calories, data=subset(data, Store == 'Zehrs'))

plot(Price ~ NV_Calories, main="Price vs Calories for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Fat (g)
```{r}
model <- lm(Price ~ NV_Fat_g, data=subset(data, Store == 'Zehrs'))

plot(Price ~ NV_Fat_g, main="Price vs Fat (g) for Zehrs", data=subset(data, Store == 'Zehrs'))
```


# Price vs Sodium (mg)
```{r}
model <- lm(Price ~ NV_Sodium_mg, data=subset(data, Store == 'Zehrs'))

plot(Price ~ NV_Sodium_mg, main="Price vs Sodium (mg) for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Carbohydrates (g)
```{r}
model <- lm(Price ~ NV_Carbohydrates_g, data=subset(data, Store == 'Zehrs'))

plot(Price ~ NV_Carbohydrates_g, main="Price vs Carbohydrates (g) for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Sugars (g)
```{r}
model <- lm(Price ~ NV_Sugars_g, data=subset(data, Store == 'Zehrs'))

plot(Price ~ NV_Sugars_g, main="Price vs Sugars (g) for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Protein (g)
```{r}
model <- lm(Price ~ NV_Protein_g, data=subset(data, Store == 'Zehrs'))

plot(Price ~ NV_Protein_g, main="Price vs Protein (g) for Zehrs", data=subset(data, Store == 'Zehrs'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```






## Metro
# Price vs Volume per unit (mL)
```{r}
model <- lm(Price ~ Volume_per_unit_mL, data=subset(data, Store == 'Metro'))

plot(Price ~ Volume_per_unit_mL, main="Price vs Volume per unit (mL) for Metro", data=subset(data, Store == 'Metro'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Total Volume (mL)
```{r}
model <- lm(Price ~ Total_Vol_mL, data=subset(data, Store == 'Metro'))

plot(Price ~ Total_Vol_mL, main="Price vs Total Volume (mL) for Metro", data=subset(data, Store == 'Metro'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Nutritional Value Base (mL)
```{r}
model <- lm(Price ~ Nutritional_Value_Base_mL, data=subset(data, Store == 'Metro'))

plot(Price ~ Nutritional_Value_Base_mL, main="Price vs Nutritional Value Base (mL) for Metro", data=subset(data, Store == 'Metro'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Calories
```{r}
model <- lm(Price ~ NV_Calories, data=subset(data, Store == 'Metro'))

plot(Price ~ NV_Calories, main="Price vs Calories for Metro", data=subset(data, Store == 'Metro'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Fat (g)
```{r}
model <- lm(Price ~ NV_Fat_g, data=subset(data, Store == 'Metro'))

plot(Price ~ NV_Fat_g, main="Price vs Fat (g) for Metro", data=subset(data, Store == 'Metro'))
```


# Price vs Sodium (mg)
```{r}
model <- lm(Price ~ NV_Sodium_mg, data=subset(data, Store == 'Metro'))

plot(Price ~ NV_Sodium_mg, main="Price vs Sodium (mg) for Metro", data=subset(data, Store == 'Metro'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Carbohydrates (g)
```{r}
model <- lm(Price ~ NV_Carbohydrates_g, data=subset(data, Store == 'Metro'))

plot(Price ~ NV_Carbohydrates_g, main="Price vs Carbohydrates (g) for Metro", data=subset(data, Store == 'Metro'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Sugars (g)
```{r}
model <- lm(Price ~ NV_Sugars_g, data=subset(data, Store == 'Metro'))

plot(Price ~ NV_Sugars_g, main="Price vs Sugars (g) for Metro", data=subset(data, Store == 'Metro'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Protein (g)
```{r}
model <- lm(Price ~ NV_Protein_g, data=subset(data, Store == 'Metro'))

plot(Price ~ NV_Protein_g, main="Price vs Protein (g) for Metro", data=subset(data, Store == 'Metro'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```







## Metro
# Price vs Volume per unit (mL)
```{r}
model <- lm(Price ~ Volume_per_unit_mL, data=subset(data, Store == 'No-Frills'))

plot(Price ~ Volume_per_unit_mL, main="Price vs Volume per unit (mL) for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Total Volume (mL)
```{r}
model <- lm(Price ~ Total_Vol_mL, data=subset(data, Store == 'No-Frills'))

plot(Price ~ Total_Vol_mL, main="Price vs Total Volume (mL) for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Nutritional Value Base (mL)
```{r}
model <- lm(Price ~ Nutritional_Value_Base_mL, data=subset(data, Store == 'No-Frills'))

plot(Price ~ Nutritional_Value_Base_mL, main="Price vs Nutritional Value Base (mL) for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Calories
```{r}
model <- lm(Price ~ NV_Calories, data=subset(data, Store == 'No-Frills'))

plot(Price ~ NV_Calories, main="Price vs Calories for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Fat (g)
```{r}
model <- lm(Price ~ NV_Fat_g, data=subset(data, Store == 'No-Frills'))

plot(Price ~ NV_Fat_g, main="Price vs Fat (g) for No-Frills", data=subset(data, Store == 'No-Frills'))
```


# Price vs Sodium (mg)
```{r}
model <- lm(Price ~ NV_Sodium_mg, data=subset(data, Store == 'No-Frills'))

plot(Price ~ NV_Sodium_mg, main="Price vs Sodium (mg) for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Carbohydrates (g)
```{r}
model <- lm(Price ~ NV_Carbohydrates_g, data=subset(data, Store == 'No-Frills'))

plot(Price ~ NV_Carbohydrates_g, main="Price vs Carbohydrates (g) for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Sugars (g)
```{r}
model <- lm(Price ~ NV_Sugars_g, data=subset(data, Store == 'No-Frills'))

plot(Price ~ NV_Sugars_g, main="Price vs Sugars (g) for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```


# Price vs Protein (g)
```{r}
model <- lm(Price ~ NV_Protein_g, data=subset(data, Store == 'No-Frills'))

plot(Price ~ NV_Protein_g, main="Price vs Protein (g) for No-Frills", data=subset(data, Store == 'No-Frills'))

abline(a = model$coefficients[1], b = model$coefficients[2], col="blue")
```